Estimating duration in the presence of misclassification

### 2024-02-08 transmission.tex
proof read ATACCC
better justify only local transmission

% Throughout this chapter, the CIS data will be stratified into the regions of England and the following age groups.
% \begin{enumerate}
%     \item $[0, 11)$: children of pre-school and primary school age.
%     \item $[11, 16)$: children of compulsory secondary-school age.
%     \item $[16, 25)$: adolescents and young adults who may remain in formal education.
%     \item $[25, 50)$: younger working age adults.
%     \item $[50, 70)$: older working age adults.
%     \item $[70, \infty)$: elderly.
% \end{enumerate}
% These groupings align closely with those previously used for analysis of the CIS data~\autocites[e.g.:][]{houseInferring}{walkerTracking}.

@@

I model each region fully independently, \ie with no shared parameters or transmission between regions.
As well as the motivation given in \cref{E-backcalc}, independent regions allows heterogeneity in the parameters between regions, which could arise from a range of socioeconomic factors.
Furthermore, the assumption of homogeneous mixing within age groups is more plausible for regions than the whole of England.
By modelling each region independently, I assume that the epidemics in each region do not interact.
Clearly, this is not realistic as travel between regions of England is common and unrestricted.
However, for a large epidemic, the non-interaction is a good approximation~\autocite{birrellRealtimea}.

>>>>

% Throughout this chapter, the CIS data will be stratified into the regions of England and the following age groups.
% \begin{enumerate}
%     \item $[0, 11)$: children of pre-school and primary school age.
%     \item $[11, 16)$: children of compulsory secondary-school age.
%     \item $[16, 25)$: adolescents and young adults who may remain in formal education.
%     \item $[25, 50)$: younger working age adults.
%     \item $[50, 70)$: older working age adults.
%     \item $[70, \infty)$: elderly.
% \end{enumerate}
% These groupings align closely with those previously used for analysis of the CIS data~\autocite[e.g.:][]{houseInferring}{walkerTracking}.

@@

I model each region fully independently, \ie with no shared parameters or transmission between regions.
As well as the motivation given in \cref{E-backcalc}, independent regions allows heterogeneity in the parameters between regions, which could arise from a range of socioeconomic factors.
Furthermore, the assumption of homogeneous mixing within age groups is more plausible for regions than the whole of England.
By modelling each region independently, I assume that the epidemics in each region do not interact.
Clearly, this is not realistic as travel between regions of England is common and unrestricted.
However, except in an epidemic's early stages, the interaction between large regions has a negligible impact on the epidemics progression~\autocite[e.g.][]{birrellRealtimea,gogSpatial,eggoSpatial}.
